---
title: "Final Project"
author: "Qiang Yang"
date: "5/2/2021"
output: html_document
---

## Imports

```{r}
library(ggplot2) 
library(shiny)
library(plotly)
library(tidyr)
library(dplyr)
library(countrycode)
library(readr)
library(tidyverse)
library(highcharter) 
library(shinyWidgets)
```

## Data Cleaning

```{r}
df_com <- read.csv("./crunchbase-data/companies.csv")
df_acq <- read.csv("./crunchbase-data/acquisitions.csv")
drop <- c("permalink", "homepage_url")
acq <- df_acq%>%
  select(name = company_name, price_amount)
companies <- df_com[, !(names(df_com) %in% drop)]
companies$first_funding_year <- format(as.Date(companies$first_funding_at), "%Y")
companies$last_funding_year <-
  format(as.Date(companies$last_funding_at), "%Y") 
companies <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a"), sep = "\\|", extra = "drop")%>%
  pivot_longer(cols = starts_with("cat"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))%>%
  filter(country_code == "USA")%>%
  ungroup()



#companies
df_companies_acq <- companies%>%
  filter(status == "acquired")
# Companies (acquired status) with price_amount
companies_acq <- left_join(df_companies_acq, acq, by = c("name"))
df_inv <- read.csv("./crunchbase-data/investments.csv")
df_inv_fund <- df_inv%>%
  select(name = company_name, investor_name, funding_round_type, funding_round_code, funded_at, raised_amount_usd)
df_inv2<- df_inv_fund%>%
  select(-c("funding_round_type", "funding_round_code"))%>%
  separate("funded_at", c("funded_Year", "Month", "Day"), sep = "-")%>%
  select(-c("Month", "Day"))%>%
  group_by(name, investor_name, funded_Year)%>%
  summarise(raised_amount_usd = sum(raised_amount_usd))
# Investment
investor <- left_join(df_inv2, companies, by = "name")

```

```{r}
investor
```

## Companies Treemap

```{r}
companies$category <- as.factor(companies$category)
companies$last_funding_year <- as.numeric(companies$last_funding_year)
ui <- fluidPage(
  titlePanel("Companies Treemap"),

  sidebarLayout(
    sidebarPanel(



      sliderInput("year", "funding year",
                  min = 2013,
                  max = 2015,
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 1000)
      )
    ),
    mainPanel(
      highchartOutput("treemap")
    )
)
)

server <- function(input, output) {

  output$treemap <- renderHighchart ({
    co <- companies%>%
      filter(last_funding_year == input$year)
    co <- aggregate(as.numeric(co$funding_total_usd), by = list(category = co$category),
                    FUN = median, na.rm = TRUE)
    names(co)[2] <- "funding_median_usd"

    hi <- co[order(co$funding_median_usd, decreasing = TRUE), ]


    hi %>%
      mutate(category = fct_reorder(category, funding_median_usd))
    
    hi <- head(hi, 20)
    hi%>%
      hchart(
        "treemap",
        hcaes(x = category, value = funding_median_usd, color = funding_median_usd))%>%
      hc_colorAxis(stops = color_stops(colors = viridis::inferno(10)))


  })


}

shinyApp(ui, server)

```

## Investors Barplots

```{r}
con_status <- factor(c('operating', 'acquired', 'ipo'))
investor$investor_name<- as.factor(investor$investor_name)
investor <- investor%>%
  ungroup()%>%
  filter(country_code == "USA")%>%
  select(investor_name, category, funded_Year, raised_amount_usd)

investor$category <- as.factor(investor$category)

ui <- fluidPage(
  titlePanel('Highest Funding Median per Industry'),
  sliderInput("year", "Year",
                  min = 2013,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)),
  selectizeInput(
    inputId = "category",
    label = "Select a category",
    choices = unique(investor$category),
    selected = '',
    multiple = TRUE
  ),
  plotlyOutput("bars")
)


server <- function(input, output, session) {
  
  output$bars <- renderPlotly({
      data <- investor %>%
      filter(funded_Year %in% input$year)%>%
      filter(category %in% input$category)
      data_2 <- data %>%
          mutate(investor_name = fct_reorder(investor_name, funding_median_usd))
      ggplot(data_2[1:20,], aes(x = investor_name, y = funding_median_usd, fill = investor_name)) + 
          geom_text(aes(y = funding_median_usd, 
                        label = paste0("$", funding_median_usd), hjust=0), size = 3) +
          geom_bar(stat = "identity")+
          coord_flip()+
          labs(x = "Roles", y = "Compensation (US Dollars)")+
          ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
          theme(legend.title = element_blank(), legend.position = "none")  })
  

}

shinyApp(ui, server)

```

EDA: \#\# Interactive plots

```{r}
investor <- investor%>%
  ungroup()%>%
  filter(country_code == "USA")%>%
  select(investor_name, category, funded_Year, raised_amount_usd)

investor$category <- as.factor(investor$category)
investor$investor_name <- as.factor(investor$investor_name)


inv_1 <- investor%>%
      filter(funded_Year == 2013)
inv_1 <- aggregate(as.numeric(inv_1$raised_amount_usd), by = list(category = inv_1$category),
                    FUN = sum, na.rm = TRUE)
names(inv_1)[2] <- "raised_total"
hi_1 <- inv_1[order(inv_1$raised_total, decreasing = TRUE), ]
hi_1 %>%
    mutate(category = fct_reorder(category, raised_total))
hi_1 <- head(hi_1, 30)

ui <- fluidPage(
  titlePanel('Highest Funding Median per Industry'),
  sliderInput("year", "Year",
                  min = 2013,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)),
  selectizeInput(
    inputId = "category",
    label = "Select a category",
    choices = unique(hi_1$category),
    selected = '',
    multiple = FALSE
  ),
  plotlyOutput("bars"),
  highchartOutput("treemap")
)


server <- function(input, output, session) {
  
  output$bars <- renderPlotly({
    inv <- investor%>%
      filter(funded_Year %in% input$year)
    inv <- aggregate(as.numeric(inv$raised_amount_usd), by = list(category = inv$category),
                    FUN = sum, na.rm = TRUE)
    names(inv)[2] <- "raised_total"

    hi <- inv[order(inv$raised_total, decreasing = TRUE), ]

    hi<- hi %>%
      mutate(category = fct_reorder(category, raised_total))
    
    hi <- head(hi, 20)
    hi%>%
    plot_ly(source = "bar_plot",
            hoverlabel  = list(bgcolor = "yellow",
                               font = list(color = "red")),
            type = "bar")%>%
      add_bars(y = ~category, x = ~raised_total, color = ~category, hoverinfo = "x+y")
    #   inv <- investor %>%
    #   filter(funded_Year %in% input$year)
    #   inv <- aggregate(inv$raised_amount_usd, by = list(category = inv$category), FUN = sum, na.rm = TRUE)
    #  hi_inv <-  inv[order(inv$raised_amount_usd, descreasing = TRUE),]
    # 
    # hi %>%
    #   mutate(category = fct_reorder(category, raised_amount_usd))
    # 
    # hi <- head(hi, 20)
    # hi%>%
    # plot_ly(source = "bar_plot",
    #         hoverlabel  = list(bgcolor = "blue",
    #                            font = list(color = "black")))%>%
    #   add_bars(x = category, y = raised_amount_usd, fill = category, hoverinfo = "x+y")
    # 
    # 
    # 
    #   ggplot(data_2[1:20,], aes(x = investor_name, y = funding_median_usd, fill = investor_name)) + 
    #       geom_text(aes(y = funding_median_usd, 
    #                     label = paste0("$", funding_median_usd), hjust=0), size = 3) +
    #       geom_bar(stat = "identity")+
    #       coord_flip()+
    #       labs(x = "Roles", y = "Compensation (US Dollars)")+
    #       ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
    #       theme(legend.title = element_blank(), legend.position = "none")  
    })
  

}

shinyApp(ui, server)




```

## Investors (Treemap)

```{r}
'
hi <- investor %>%
  filter(funded_Year == 2007)
hi <- aggregate(as.numeric(hi$funding_total_usd),
         by=list(category=hi$category),
                FUN=sum, na.rm=TRUE)
hi
names(hi)[2] <- "funding_median_usd"
hi <- hi[order(hi$funding_median_usd, decreasing = TRUE),]
hi
hi <- hi[1:20,]
hi %>%
    mutate(category = fct_reorder(category, funding_median_usd))%>%
    ggplot(aes(x = category, y = funding_median_usd, fill = category)) +
    geom_text(aes(y = funding_median_usd,
                  label = paste0("$", funding_median_usd), hjust=0), size = 3) +
    geom_bar(stat = "identity")+
    coord_flip()+
    labs(x = "Roles", y = "Compensation (US Dollars)")+
    ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
    theme(legend.title = element_blank(), legend.position = "none")
'
'
hi <- investor %>%
  filter(funded_Year == 2007) %>%
   group_by(investor_name) %>%
   summarise(num_companies=n_distinct(name))
hi
'
```

## Plotly_shiny

```{r}
con_status <- factor(c('operating', 'acquired', 'ipo'))

ui <- fluidPage(
  titlePanel('Highest Funding Median per Industry'),
  sliderInput("year", "Year",
                  min = 2013,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)),
  selectizeInput(
    inputId = "status",
    label = "Select a status",
    choices = unique(con_status),
    selected = 'operating',
    multiple = TRUE
  ),
  plotlyOutput("bars")
  # verbatimTextOutput("click")
)


server <- function(input, output, session) {
  
  output$bars <- renderPlotly({
      data <- operating_investor %>%
      filter(funded_Year %in% input$year)%>%
      filter(status %in% input$status)
     
      data <- aggregate(as.numeric(data$funding_total_usd), 
           by=list(category=data$category), FUN=median, na.rm=TRUE)
      names(data)[2] <- "funding_median_usd" 
      
      hi <- data[order(data$funding_median_usd, decreasing = TRUE),]
      data <- data[1:20,]
      data_2 <- data %>%
          mutate(category = fct_reorder(category, funding_median_usd))
      ggplot(data_2, aes(x = category, y = funding_median_usd, fill = category, customdata = category)) + 
          geom_text(aes(y = funding_median_usd, 
                        label = paste0("$", funding_median_usd), hjust=0), size = 3) +
          geom_bar(stat = "identity")+
          coord_flip()+
          labs(x = "Roles", y = "Compensation (US Dollars)")+
          ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
          theme(legend.title = element_blank(), legend.position = "none")  })
  
  # output$click <- renderPrint({
  #   d <- event_data("plotly_click")
  #   if (is.null(d)) return("Click a bar")
  #   data_2 %>%
  #     filter(category %in% d$customdata)
  # })
  
}

shinyApp(ui, server)

```

```{r}

con_status <- factor(c('operating', 'acquired', 'ipo'))
ui <- fluidPage(
  titlePanel('Highest Funding Median per Industry'),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("status",
                         "Choose status", 
                         choices = levels(con_status),
                         selected = levels(con_status)),
      sliderInput("year", "Year",
                  min = 2013,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)
      )
    ),
    mainPanel(
      #highchartOutput("fund_median"),
      plotOutput(outputId = "fund_median")
    )
  )
)

server <- function(input, output) {
  output$fund_median <- renderPlot({
      
      data <- operating_investor %>%
        filter(funded_Year %in% input$year) %>%
        filter(status  %in% input$status)
     
      data <- aggregate(as.numeric(data$funding_total_usd), 
           by=list(category=data$category), FUN=median, na.rm=TRUE)
      names(data)[2] <- "funding_median_usd" 
      
      hi <- data[order(data$funding_median_usd, decreasing = TRUE),]
      data <- data[1:20,]
      data %>%
          mutate(category = fct_reorder(category, funding_median_usd))%>%
          ggplot(aes(x = category, y = funding_median_usd, fill = category)) + 
          geom_text(aes(y = funding_median_usd, 
                        label = paste0("$", funding_median_usd), hjust=0), size = 3) +
          geom_bar(stat = "identity")+
          coord_flip()+
          labs(x = "Roles", y = "Compensation (US Dollars)")+
          ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
          theme(legend.title = element_blank(), legend.position = "none")
        
    })  
      
}
  

'
server <- function(input, output) {
  
  output$fund_median <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status)
    data <- aggregate(as.numeric(data$funding_total_usd), 
         by=list(category=data$category), FUN=median, na.rm=TRUE)
    names(data)[2] <- "funding_median_usd" 
    data %>%
      hchart(
        "treemap", 
        hcaes(x = category, value = funding_median_usd, color = funding_median_usd)
      )
  })
}
'
shinyApp(ui, server)
```

```{r}
con_status <- factor(c('operating', 'acquired', 'ipo'))
con_category <- factor(unique(investor[c("category")])$category)
ui <- fluidPage(
  titlePanel('Top Investors Based on Category'),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("status",
                         "Choose status", 
                         choices = levels(con_status),
                         selected = levels(con_status)),
                   
       pickerInput(
            "category",
            "Choose category",
            choices = unique(levels(con_category)),
            options = list('action-box' = TRUE),
            multiple=TRUE,
            selected=con_category[1]
        ),
      sliderInput("year", "Year",
                  min = 2010,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2010,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)
      )
    ),
    mainPanel(
      highchartOutput("invest_category"),
      #highchartOutput("invest_category_money"),
    )
  )
)
  
server <- function(input, output) {
  
  
  output$invest_category <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status)# %>%
      filter(category  %in% input$category) %>%
      group_by(investor_name) %>%
      summarise(num_companies=n_distinct(name))
    data %>%
      hchart(
        "treemap", 
        hcaes(x = investor_name, value = num_companies, color = num_companies)
      )
  })
  
  # output$invest_category_money <- renderHighchart ({ 
  #   data <- investor %>%
  #     filter(funded_Year %in% input$year) %>%
  #     filter(status  %in% input$status) %>%
  #     filter(category  %in% input$category)
  #   
  #   data <- aggregate(as.numeric(data$funding_total_usd), 
  #        by=list(category=data$category), FUN=median, na.rm=TRUE)
  #   names(data)[2] <- "funding_median_usd" 
  #   data %>%
  #     hchart(
  #       "treemap", 
  #       hcaes(x = investor_name, funding_median_usd, color = funding_median_usd)
  #     )
  # })
}
shinyApp(ui, server)
```

``` {.{.{.{'}}}}
{r, warning=FALSE, echo=FALSE}
con <- factor(unique(levels_df[c("title")])$title)
con2 <- factor(unique(levels_df[c("state")])$state)
ui <-
  fluidPage(
    # App title
    titlePanel("Common Investors based on category"),
    
    # sidebar layout with input and output definitions
    sidebarLayout(
      # Sidebar panel for inputs
      sidebarPanel(
        sliderInput("yoe",
                    "Years of experience",
                    min = min(levels_df$yearsofexperience),
                    max = 30,
                    value = c(min(levels_df$yearsofexperience), 
                              30),
                    step = 1,
                    sep = ""),
         pickerInput(
            "statePicker",
            "Select/deselect all + format selected",
            choices = unique(levels(con2)),
            options = list("action-box" = TRUE),
            multiple=TRUE,
            selected="WA"
        ),
      ),
     
      
      # Main panel for displaying outputs
      mainPanel(
        plotOutput(outputId = "tc")
      )
    ))
server <- function(input, output) {
  output$tc <-
    renderPlot({
      
      prep <- levels_df %>% 
        filter(yearsofexperience >= input$yoe[1] & 
              yearsofexperience <= input$yoe[2])
    
      location_df <- prep %>% 
        distinct(state, .keep_all = TRUE) %>%
        select(state, zip, lat, long) %>% na.omit()
      tc <- prep
      if(length(input$statePicker) != 0) {
        tc <- tc %>%  
          filter(state %in% input$statePicker) 
      } 
      tc <- aggregate(list(tc = tc$totalyearlycompensation,
                           basesalary = tc$basesalary,
                           stockgrantvalue = tc$stockgrantvalue,
                           bonus = tc$bonus), 
                          by=list(title=tc$title), 
                          FUN=mean, na.action = na.omit)
      tc %>%
        mutate(title = fct_reorder(title, tc))%>%
        ggplot(aes(x = title, y = tc, fill = title)) + 
        geom_text(aes(y = tc, label = paste0("$", round(tc, 2)), hjust=0), size = 3) +
        geom_bar(stat = "identity")+
        coord_flip()+
        labs(x = "Roles", y = "Compensation (US Dollars)")+
        ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
        theme(legend.title = element_blank(), legend.position = "none")
        
    })  
      
}
shinyApp(ui, server)
'
```

-   Investor side:

    -   Status (left_join company_name), company_catogories, investor_name, raised_amount_usd, (funded_at)

    -   funding_round_type, funding_round_code

    -   Treemap

        -   X axis: Category

        -   Y axis: \# investors (median) or funding median

        -   Label: Funding Total, Funding Median, \# of companies

        -   Scroller: Year

        -   Selector: Funding Round, Status

    -   Interactive Barplot (Flipped) - Top 15 or 20

        -   Selector (Filter)

            -   Year

            -   Location

            -   Category

        -   X axis: Investors

        -   Y axis: funding total (Label: \# of companies funded by each investors)
