---
title: "Final Project"
author: "Qiang Yang"
date: "5/2/2021"
output: html_document
---

## Imports

```{r}
library(ggplot2) 
library(shiny)
library(plotly)
library(tidyr)
library(dplyr)
library(countrycode)
library(readr)
library(tidyverse)
library(highcharter) 
library(shinyWidgets)
```

## Data Cleaning

```{r}
df_com <- read.csv("./crunchbase-data/companies.csv")
df_acq <- read.csv("./crunchbase-data/acquisitions.csv")
drop <- c("permalink", "homepage_url", "city")

acq <- df_acq%>%
  select(name = company_name, price_amount)



companies = df_com[, !(names(df_com) %in% drop)]
companies$first_funding_year <- format(as.Date(companies$first_funding_at), "%Y")
companies$last_funding_year <-
  format(as.Date(companies$last_funding_at), "%Y")

companies <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat_a"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
companies<- companies %>% select(-contains("cat_"))

'
hi <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat_a"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
hi <- hi %>% select(-contains("cat_"))
hi
'
# Companies dataframe
'
companies <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
'
#companies

df_companies_acq <- companies%>%
  filter(status == "acquired")

# Companies (acquired status) with price_amount
companies_acq <- left_join(df_companies_acq, acq, by = c("name"))



df_inv <- read.csv("./crunchbase-data/investments.csv")
df_inv_fund <- df_inv%>%
  select(name = company_name, investor_name, funding_round_type, funding_round_code, funded_at, raised_amount_usd)

df_inv2<- df_inv_fund%>%
  select(-c("funding_round_type", "funding_round_code"))%>%
  separate("funded_at", c("funded_Year", "Month", "Day"), sep = "-")%>%
  select(-c("Month", "Day"))%>%
  group_by(name, investor_name, funded_Year)%>%
  summarise(raised_amount_usd = sum(raised_amount_usd))


# Investment
investor <- left_join(df_inv2, companies, by = "name")
  # separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  # pivot_longer(cols = starts_with("cat"),
  #              names_to = "cate",
  #              values_to = "category",
  #              values_drop_na = TRUE)%>%
  # select(-c("cate"))
```

EDA:

```{r}
companies
```

```{r}
companies_acq
```

```{r}
investor
```

```{r}
investor <- investor %>%
  filter(as.numeric(last_funding_year) >= 2013)

investor <- investor[!is.na(investor$raised_amount_usd), ]
operating_investor <- investor %>% filter(status == "operating")
operating_investor
```

## Investors (Treemap)

```{r}
'
hi <- investor %>%
  filter(funded_Year == 2007) 
hi <- aggregate(as.numeric(hi$funding_total_usd), 
         by=list(category=hi$category), 
                FUN=sum, na.rm=TRUE)
hi
names(hi)[2] <- "funding_median_usd" 
hi <- hi[order(hi$funding_median_usd, decreasing = TRUE),]
hi
hi <- hi[1:20,]
hi %>%
    mutate(category = fct_reorder(category, funding_median_usd))%>%
    ggplot(aes(x = category, y = funding_median_usd, fill = category)) + 
    geom_text(aes(y = funding_median_usd, 
                  label = paste0("$", funding_median_usd), hjust=0), size = 3) +
    geom_bar(stat = "identity")+
    coord_flip()+
    labs(x = "Roles", y = "Compensation (US Dollars)")+
    ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
    theme(legend.title = element_blank(), legend.position = "none")
'
'
hi <- investor %>%
  filter(funded_Year == 2007) %>%
   group_by(investor_name) %>%
   summarise(num_companies=n_distinct(name))
hi
'
```

```{r}

con_status <- factor(c('operating', 'acquired', 'ipo'))
ui <- fluidPage(
  titlePanel('Highest Funding Median per Industry'),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("status",
                         "Choose status", 
                         choices = levels(con_status),
                         selected = levels(con_status)),
      sliderInput("year", "Year",
                  min = 2013,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2013,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)
      )
    ),
    mainPanel(
      #highchartOutput("fund_median"),
      plotOutput(outputId = "fund_median")
    )
  )
)

server <- function(input, output) {
  output$fund_median <- renderPlot({
      
      data <- operating_investor %>%
        filter(funded_Year %in% input$year) %>%
        filter(status  %in% input$status)
     
      data <- aggregate(as.numeric(data$funding_total_usd), 
           by=list(category=data$category), FUN=median, na.rm=TRUE)
      names(data)[2] <- "funding_median_usd" 
      
      hi <- data[order(data$funding_median_usd, decreasing = TRUE),]
      data <- data[1:20,]
      data %>%
          mutate(category = fct_reorder(category, funding_median_usd))%>%
          ggplot(aes(x = category, y = funding_median_usd, fill = category)) + 
          geom_text(aes(y = funding_median_usd, 
                        label = paste0("$", funding_median_usd), hjust=0), size = 3) +
          geom_bar(stat = "identity")+
          coord_flip()+
          labs(x = "Roles", y = "Compensation (US Dollars)")+
          ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
          theme(legend.title = element_blank(), legend.position = "none")
        
    })  
      
}
  

'
server <- function(input, output) {
  
  output$fund_median <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status)
    data <- aggregate(as.numeric(data$funding_total_usd), 
         by=list(category=data$category), FUN=median, na.rm=TRUE)
    names(data)[2] <- "funding_median_usd" 
    data %>%
      hchart(
        "treemap", 
        hcaes(x = category, value = funding_median_usd, color = funding_median_usd)
      )
  })
}
'
shinyApp(ui, server)
```

```{r}
con_status <- factor(c('operating', 'acquired', 'ipo'))
con_category <- factor(unique(investor[c("category")])$category)
ui <- fluidPage(
  titlePanel('Top Investors Based on Category'),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("status",
                         "Choose status", 
                         choices = levels(con_status),
                         selected = levels(con_status)),
                   
       pickerInput(
            "category",
            "Choose category",
            choices = unique(levels(con_category)),
            options = list('action-box' = TRUE),
            multiple=TRUE,
            selected=con_category[1]
        ),
      sliderInput("year", "Year",
                  min = 2010,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2010,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)
      )
    ),
    mainPanel(
      highchartOutput("invest_category"),
      #highchartOutput("invest_category_money"),
    )
  )
)
  
server <- function(input, output) {
  
  
  output$invest_category <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status)# %>%
      filter(category  %in% input$category) %>%
      group_by(investor_name) %>%
      summarise(num_companies=n_distinct(name))
    data %>%
      hchart(
        "treemap", 
        hcaes(x = investor_name, value = num_companies, color = num_companies)
      )
  })
  
  output$invest_category_money <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status) %>%
      filter(category  %in% input$category)
    
    data <- aggregate(as.numeric(data$funding_total_usd), 
         by=list(category=data$category), FUN=median, na.rm=TRUE)
    names(data)[2] <- "funding_median_usd" 
    data %>%
      hchart(
        "treemap", 
        hcaes(x = investor_name, funding_median_usd, color = funding_median_usd)
      )
  })
}
shinyApp(ui, server)
```

``` {.{.{.{.{'}}}}}
{r, warning=FALSE, echo=FALSE}
con <- factor(unique(levels_df[c("title")])$title)
con2 <- factor(unique(levels_df[c("state")])$state)
ui <-
  fluidPage(
    # App title
    titlePanel("Common Investors based on category"),
    
    # sidebar layout with input and output definitions
    sidebarLayout(
      # Sidebar panel for inputs
      sidebarPanel(
        sliderInput("yoe",
                    "Years of experience",
                    min = min(levels_df$yearsofexperience),
                    max = 30,
                    value = c(min(levels_df$yearsofexperience), 
                              30),
                    step = 1,
                    sep = ""),
         pickerInput(
            "statePicker",
            "Select/deselect all + format selected",
            choices = unique(levels(con2)),
            options = list("action-box" = TRUE),
            multiple=TRUE,
            selected="WA"
        ),
      ),
     
      
      # Main panel for displaying outputs
      mainPanel(
        plotOutput(outputId = "tc")
      )
    ))
server <- function(input, output) {
  output$tc <-
    renderPlot({
      
      prep <- levels_df %>% 
        filter(yearsofexperience >= input$yoe[1] & 
              yearsofexperience <= input$yoe[2])
    
      location_df <- prep %>% 
        distinct(state, .keep_all = TRUE) %>%
        select(state, zip, lat, long) %>% na.omit()
      tc <- prep
      if(length(input$statePicker) != 0) {
        tc <- tc %>%  
          filter(state %in% input$statePicker) 
      } 
      tc <- aggregate(list(tc = tc$totalyearlycompensation,
                           basesalary = tc$basesalary,
                           stockgrantvalue = tc$stockgrantvalue,
                           bonus = tc$bonus), 
                          by=list(title=tc$title), 
                          FUN=mean, na.action = na.omit)
      tc %>%
        mutate(title = fct_reorder(title, tc))%>%
        ggplot(aes(x = title, y = tc, fill = title)) + 
        geom_text(aes(y = tc, label = paste0("$", round(tc, 2)), hjust=0), size = 3) +
        geom_bar(stat = "identity")+
        coord_flip()+
        labs(x = "Roles", y = "Compensation (US Dollars)")+
        ggtitle(paste("Factoring YOE + Location: Pay for roles"))+
        theme(legend.title = element_blank(), legend.position = "none")
        
    })  
      
}
shinyApp(ui, server)
'
```

-   Investor side:

    -   Status (left_join company_name), company_catogories, investor_name, raised_amount_usd, (funded_at)

    -   funding_round_type, funding_round_code

    -   Treemap

        -   X axis: Category

        -   Y axis: \# investors (median) or funding median

        -   Label: Funding Total, Funding Median, \# of companies

        -   Scroller: Year

        -   Selector: Funding Round, Status

    -   Interactive Barplot (Flipped) - Top 15 or 20

        -   Selector (Filter)

            -   Year

            -   Location

            -   Category

        -   X axis: Investors

        -   Y axis: funding total (Label: \# of companies funded by each investors)
