---
title: "Final Project"
author: "Qiang Yang"
date: "5/2/2021"
output: html_document
---

## Imports

```{r}
library(ggplot2) 
library(shiny)
library(plotly)
library(tidyr)
library(dplyr)
library(countrycode)
library(readr)
library(tidyverse)
library(highcharter) 
```

## Data Cleaning

```{r}
df_com <- read.csv("./crunchbase-data/companies.csv")
df_acq <- read.csv("./crunchbase-data/acquisitions.csv")
drop <- c("permalink", "homepage_url", "city")

acq <- df_acq%>%
  select(name = company_name, price_amount)



companies = df_com[, !(names(df_com) %in% drop)]
companies$first_funding_year <- format(as.Date(companies$first_funding_at), "%Y")
companies$last_funding_year <-
  format(as.Date(companies$last_funding_at), "%Y")

companies <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat_a"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
companies<- companies %>% select(-contains("cat_"))

'
hi <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat_a"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
hi <- hi %>% select(-contains("cat_"))
hi
'
# Companies dataframe
'
companies <- companies%>%
  select(-c(first_funding_at, last_funding_at))%>%
  separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  pivot_longer(cols = starts_with("cat"),
               names_to = "cate",
               values_to = "category",
               values_drop_na = TRUE)%>%
  select(-c("cate"))
'
#companies

df_companies_acq <- companies%>%
  filter(status == "acquired")

# Companies (acquired status) with price_amount
companies_acq <- left_join(df_companies_acq, acq, by = c("name"))



df_inv <- read.csv("./crunchbase-data/investments.csv")
df_inv_fund <- df_inv%>%
  select(name = company_name, investor_name, funding_round_type, funding_round_code, funded_at, raised_amount_usd)

df_inv2<- df_inv_fund%>%
  select(-c("funding_round_type", "funding_round_code"))%>%
  separate("funded_at", c("funded_Year", "Month", "Day"), sep = "-")%>%
  select(-c("Month", "Day"))%>%
  group_by(name, investor_name, funded_Year)%>%
  summarise(raised_amount_usd = sum(raised_amount_usd))


# Investment
investor <- left_join(df_inv2, companies, by = "name")
  # separate(category_list, c("cat_a", "cat_b", "cat_c", "cat_d", "cat_e", "cat_f", "cat_g", "cat_h", "cat_i", "cat_j", "cat_k", "cat_l", "cat_m"), sep = "\\|", extra = "merge", fill = "right")%>%
  # pivot_longer(cols = starts_with("cat"),
  #              names_to = "cate",
  #              values_to = "category",
  #              values_drop_na = TRUE)%>%
  # select(-c("cate"))
```

EDA:

```{r}
companies
```

```{r}
companies_acq
```

```{r}
investor
```

## Investors (Treemap)

```{r}
#investor %>%
#  filter(category == "Billing")
```

```{r}
hi <- investor %>%
  filter(funded_Year == 2007) 
  aggregate(as.numeric(hi$funding_total_usd), 
         by=list(category=hi$category), 
                FUN=sum, na.rm=TRUE)
hi
```

```{r}

con_status <- factor(c('closed', 'operating', 'acquired', 'ipo'))
ui <- fluidPage(
  titlePanel('Categories & its Investors'),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("status",
                         "Choose status", 
                         choices = levels(con_status),
                         selected = levels(con_status)),
      sliderInput("year", "Year",
                  min = 2007,
                  max = range(as.numeric(investor$funded_Year))[2],
                  value = 2007,
                  sep = "",
                  step = 1,
                  animate = animationOptions(interval = 300)
      )
    ),
    mainPanel(
      highchartOutput("investors")
    )
  )
)
  
server <- function(input, output) {
  
  output$investors <- renderHighchart ({ 
    data <- investor %>%
      filter(funded_Year %in% input$year) %>%
      filter(status  %in% input$status)
    data <- aggregate(as.numeric(data$funding_total_usd), 
         by=list(category=data$category), FUN=median, na.rm=TRUE)
    names(data)[2] <- "funding_median_usd" 
    data %>%
      hchart(
        "treemap", 
        hcaes(x = category, value = funding_median_usd, color = funding_median_usd)
      )
  })
}
shinyApp(ui, server)
```

-   Investor side:

    -   Status (left_join company_name), company_catogories, investor_name, raised_amount_usd, (funded_at)

    -   funding_round_type, funding_round_code

    -   Treemap

        -   X axis: Category

        -   Y axis: \# investors (median) or funding median

        -   Label: Funding Total, Funding Median, \# of companies

        -   Scroller: Year

        -   Selector: Funding Round, Status

    -   Interactive Barplot (Flipped) - Top 15 or 20

        -   Selector (Filter)

            -   Year

            -   Location

            -   Category

        -   X axis: Investors

        -   Y axis: funding total (Label: \# of companies funded by each investors)
